The Adaptive Multi-scale Simulation Infrastructure - Design and Application

### 2016-01-10 doc/articles/amsi_biotissue/paper.tex
more paper work

\label{amsi_scales}
A configuration file is supplied during command invocation containing the initial configuration of the process sets and their assignment to individual scales, as well as declaring the coupling between scales in the simulation. The declaration of a scale and the initialization of the process set associated with the scale are considered a single atomic operation in the current implementation. A simple configuration file can be seen in listing \ref{amsi_config_file} which declares the existence of two scales, macro and micro\_fo, and tells the amsi intialization procedures to assigne them process sets containig 64 and 8128 processes, respectively (for a total of $2^{13}$ processes). The file also specifies the scale-coupling relations, with macro coupled to micro and micro coupled to macro. Note that the order of specification is not relevant to the operation of amsi.
%
\begin{lstlisting}[caption={amsi\_config file},label=amsi_config_file]
  macro 64
  micro_fo 8128
  #
  macro micro_fo
  micro_fo macro_fo
\end{lstlisting}
%
Typically creation of this file will be automated and added to the shell script used to invoke the simulation, so ensure that process counts passed in throught the configuration file are valid. Alternative specification mechanisms such as ratio specification (equivalently percentage specification) are being considered for future use to prevent the possbility of misallocation of processes (the user not specifying assignment for all processes available to the simulation).

@@

@@

>>>>

\label{amsi_scales}
A configuration file is supplied during command invocation containing the initial configuration of the process sets and their assignment to individual scales, as well as declaring the coupling between scales in the simulation. The declaration of a scale and the initialization of the process set associated with the scale are considered a single atomic operation in the current implementation.

@@

Scales are an abstraction grouping a set of standalone scale-tasks operating on a single scale, the set may be as minimal as a single scale-task as in the case of a primary scale with many contributing tertiary scales. The set may also contain many individual scale-tasks which all operate within a single scale, such as when a primary scale-task has an associated tertiary scale which constitutes many individual simulations, as in the biotissue example case discussed in section \ref{biotissue}. Precisely what defines a scale-task is left up to the user, the intent is for each scale-task to represent a standalone single-scale simulation incorporated into the multi-scale system.

@@

A simple configuration file can be seen in listing \ref{amsi_config_file} which declares the existence of two scales, macro and micro\_fo, and tells the amsi intialization procedures to assigne them process sets containig 64 and 8128 processes, respectively (for a total of $2^{13}$ processes). The file also specifies the scale-coupling relations, with macro coupled to micro and micro coupled to macro. Note that the order of specification is not relevant to the operation of amsi.
%
\begin{lstlisting}[caption={amsi\_config file},label=amsi_config_file]
  macro 64
  micro_fo 8128
  #
  macro micro_fo
  micro_fo macro_fo
\end{lstlisting}
%
Typically creation of this file will be automated and added to the shell script used to invoke the simulation, so ensure that process counts passed in throught the configuration file are valid. Alternative specification mechanisms such as ratio specification (equivalently percentage specification) are being considered for future use to prevent the possbility of misallocation of processes (the user not specifying assignment for all processes available to the simulation).

The assignment of processes to a process set is currently static, and processes cannot be reassigned during a simulation. Additionally the assignment of a scale to a process set is static as well. However, scale-tasks are capable of being dynamically created and destroyed during runtime. Additionally, scale-tasks associated with specific subsets of a process set (either a single process or several processes) may be migrated in part or in whole. Migrating a scale-task in part amounts to using load balancing facilities on the associated processes to redistribute all data scale-task from a scale-task to a subset of the previously associated processes, allowing the freed processes to be assigned data from other scale-tasks. Migrating a scale task in whole constitutes using load balancing operations on the process set associated with the entire scale to move all pertinent data between subset of the managed process set. In the current implementation these operations are both collective on the process set associated with the managed scale.
